---
output: github_document
bibliography: vignette_biblio.bib
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r}
#include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(knitr)
```


# Largevars

The Largevars R package conducts a cointegration test for high-dimensional vector autoregressions of order $k$ 

based on the large $N,T$ asymptotics of @bykhovskaya_gorin_1, @bykhovskaya_gorin_k. The implemented test is a modification of the Johansen likelihood ratio test. In the absence of cointegration the test converges to the partial sum of the Airy$_1$ point process. This package contains simulated quantiles of the first ten partial sums of the Airy$_1$ point process that are precise up to the first $3$ digits.


## Installation

You can install the latest version of Largevars from Github:

```{r}
library(devtools)
install_github("eszter-kiss/Largevars")
library(Largevars)
```

## Example

The following example is a replication of the S\&P100 example from  @bykhovskaya_gorin_1, @bykhovskaya_gorin_k.

We use logarithms of weekly adjusted closing prices of assets in the S\&P100 over ten years (01.01.2010-01.01.2020), which gives us $\tau=522$ observations across time. The S\&P100 includes 101 stocks, with Google having two classes of stocks. We use 92 of those stocks, those for which data were available for our chosen time period. Only one of Google’s two listed stocks is kept in the sample. Therefore, $N = 92$, $T = 521$ and $T/N  \approx 5.66$. The data that we use are accessible from the ``data'' folder in the package.



```{r}
library(Largevars)

## load data
library(readr)
s_p100_price <- read_csv("data/s_p100_price_adj.csv",show_col_types = FALSE)

## Transform data according to researcher needs
dataSP <- log(s_p100_price[,seq(2,dim(s_p100_price)[2])])

## Turn data frame into numeric matrix to match function requirements
dataSP <- as.matrix(dataSP)

## Use the package documentation by calling help
?largevar

## Use largevar function
### Save the function output (list)
result <- largevar(data=dataSP,k=1,r=1,fin_sample_corr = FALSE,
      plot_output=TRUE,significance_level=0.05)

### Display the result
result
```

If we want to individually access certain values from the output list, we can do it in the usual way, by referencing the elements of the list:

```{r}
result$statistic
result$significance_test$p_value
result$significance_test$boolean_decision
result$significance_test$significance_table
```

If we want to see empirical p-value, we can use the following function:

```{r}
result2 <- sim_function(N=92,tau=522,stat_value=-0.2777,k=1,r=1,
			   fin_sample_corr = FALSE,sim_num=50)
result2
```

## Authors

Anna Bykhovskaya (Duke University) anna.bykhovskaya\@duke.edu


Vadim Gorin (University of California at Berkeley) vadicgor\@gmail.com


Eszter Kiss (Duke University) ekiss2803\@gmail.com

## Cite our package

```{r}
citation("Largevars")
```

## License

MIT License (c) 2024

## References
